A systematic search for transiting planets using \KT

### 2015-02-07 ms.tex
Hogg hacking on the intro

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ``light curve'' not ``light-curve'' or ``lightcurve''
%  * that is all.
%

@@

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
\kepler\ Mission, observing approximately a dozen fields near the ecliptic
plane, each for 75 days at a time.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques extremely valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of
the spacecraft, but (blah blah it sucks for describing the FF now).
Inference of the flat field is challenging because of the nature of the
spacecraft's observations: point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth.
Therefore, much of the effort in \KT\ is focused on the potential of the latter.

Previous studies have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
\citet{Crossfield:2015} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.

In both of these cases, the authors follow a standard procedure when working
with \kepler\ data: ``correcting'' the light curve as a step before the search
for transiting planets.
Light curves from the primary \kepler\ mission are typically de-trended to
remove the effects of stellar variability before searching for transiting
planets.
With \KT, the authors of each of these papers fit and subtract their measured
effects from the spacecraft pointing variations and stellar variability.
Such a technique can be extremely dangerous.
Small signals, such as planet transits, can be partially absorbed into the
assumed-stellar signals, making each individual transit event appear
shallower.
Small planets that should appear just above a specific signal-to-noise
threshold could then be missed because of the de-trending.

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals.
This method enables us to search for and measure exoplanet signals
independently of an estimate of the systematics, provided that the systematics
lie in the domain of the model.
The likelihood of the simultaneous fit of the systematics and transit signals
to the data can then be compared to the likelihood of the fit of the systematics
alone, reducing exoplanet ``search'' to a simple model comparison problem.

@@

Catalogs of transiting planets found by \KT\ will be important to better
understand the formation and evolution of planetary systems.
These planets, especially when they orbit especially bright or late-type stars,
will be useful targets for ground-based and space-based follow-up, both for
current facilities and those planned in the near-future such as JWST.

@@

(cite Dun AAS and in prep here).

...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
right, because the mean and variance of the Gaussian likelihood are
analytic (though maybe expensive).)  If we \emph{do} marginalize (or
maybe either way), we need to emphasize here the difference between
simultaneously \emph{estimating} the signal and the noise as opposed
to simultaneously \emph{fitting} the signal and the noise and
marginalization out of the latter.  Key idea: Don't come to a
conclusion about (estimate) anything you don't care about, if you can
possibly avoid it!

>>>>

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ``light curve'' not ``light-curve'' or ``lightcurve''
%  * Do not put in any comments that might get tweeted by @OverheardOnAph
%  * that is all.
%

@@

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
\kepler\ Mission, observing approximately a dozen fields near the ecliptic
plane, each for 75 days at a time.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or else data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of
the spacecraft, but is not nearly as accurate as required to make
pointing-insensitive photometric measurements at the relevant level of precision.
In principle direct inference of the flat-field might be possible;
however, because point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth, there isn't enough information in the data to derive or
infer a highly accurate flat-field map.
Therefore, work on \KT\ is sensibly focused on building data-analysis
techniques that are pointing-insensitive.

Previous projects have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
\citet{Crossfield:2015} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.
DFM HERE IS WHERE WE (cite Dun AAS and in prep).

In these light-curve processing methodologies,
the authors follow a traditional procedure of ``correcting'' the light curve
as a step that happens \emph{before} the search for transiting planets.
Light curves from the primary \kepler\ mission are typically de-trended to
remove the effects of stellar variability before searching for transiting
planets.
With \KT, application of the traditional methods involves fitting and subtracting measured
effects from the spacecraft pointing variations and stellar variability.
Fit-and-subtract is dangerous:
Small signals, such as planet transits, can be partially absorbed into the
best-fit stellar variability or systematics models, making each individual transit event appear
shallower; that is, the traditional methods are prone to over-fitting.
Because over-fitting will in general reduce the amplitude of true exoplanet signals,
small planets that ought to appear just above any specific signal-to-noise
or depth
threshold could be missed because of the de-trending.

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals.
Simultaneous fitting enables a search for---and measurement of---exoplanet signals
to deliver results that are 
independent of any implied estimate of the systematics, provided that the true
systematics lie in the domain of the systematics model.
DFM I WOULD SAY HERE \emph{WHY} SIMULTANEOUS FITTING LEADS TO INDEPENDENCE, AND WHAT DO YOU MEAN BY THAT?
The likelihood of the simultaneous fit of the systematics and transit signals
to the data can then be compared to the likelihood of the fit of the systematics
alone, reducing exoplanet ``search'' to a simple model comparison problem.

DFM:  HERE IS WHERE I WOULD TALK ABOUT MARGINALIZATION...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
right, because the mean and variance of the Gaussian likelihood are
analytic (though maybe expensive).)  If we \emph{do} marginalize (or
maybe either way), we need to emphasize here the difference between
simultaneously \emph{estimating} the signal and the noise as opposed
to simultaneously \emph{fitting} the signal and the noise and
marginalization out of the latter.  Key idea: Don't come to a
conclusion about (estimate) anything you don't care about, if you can
possibly avoid it!

@@

Catalogs of transiting planets found in the \KT\ data will be important to better
understand the physical properties, formation, and evolution of planetary systems.
These planets, especially when they orbit especially bright or late-type stars,
will be useful targets for ground-based and space-based follow-up, both for
current facilities and those planned in the near-future such as JWST.
They will also deliver input data for next-generation population inferences (cite DFM),
which in turn constrain population synthesis models.

@@
